The Evolution of Phenotypically Invariant Genetic Networks

### 2017-12-08 kalman_walk_paper.tex
remove apx A1 for wrongness

What are the fitness consequences?
A population of $F_2$ hybrids will begin to be substantially less fit than the parentals
once they differ from the optimum by a distance of order $\gamma$,
i.e., once $\sqrt{4 \omega T/N_e} \approx \gamma / \sigma_N$.
This implies that hybrid incompatibility among $F_2$ hybrids should appear much slower --
on a time scale of $N_e (\gamma / \sigma_N)^2 / (4 \omega)$ generations.
The $F_1$s will not suffer fitness consequences until the hybrid mean is further than $\gamma$ from the optimum;
as shown in appendix \ref{apx:away_from_opt} (and suggested by figure \ref{fig:conceptual_fig}),
this deviation of the mean from optimum grows with the square of the distance between the parental populations,
and so we expect fitness costs in $F_1$s to appear on a time scale of $N_e^2$ generations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Local expansion of the fitness surface}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Away from the optimum}
\label{apx:away_from_opt}

Let two points on $\allS$ be $x_1$ and $x_2$, let $\bar x = (x_1+x_2)/2$, and let $z=(x_2 - x_1)/2$.
Then with $\grad D^2$ and $\grad^2 D^2$ the first and second derivatives of $D^2$, respectively,
Taylor expanding about $x_1$ and $x_2$ finds that
\begin{align*}
    D(\bar x)^2 
    &= D(x_1)^2 + \grad D(x_1)^2 \cdot z + \frac{1}{2} z^T \grad^2  D(x_1)^2 z + O(\|z\|^3) \\
    &=  D(x_2)^2 - \grad D(x_2)^2 \cdot z + \frac{1}{2} z^T \grad^2  D(x_2)^2 z + O(\|z\|^3) .
\end{align*}
Now, since $ D(x_1)^2 =  D(x_2)^2 = \grad D(x_1)^2 = \grad D(x_2)^2 = 0$ and
\begin{align*}
    \grad D(x_2)^2 = \grad D(x_1)^2 + 2 z^T \grad^2  D(x_1)^2 + O(\|z\|^2), \quad \text{and} \\
    \grad^2 D(x_2)^2 = \grad^2 D(x_1)^2 + O(\|z\|), 
\end{align*}
adding together the two equations above and dividing by two gets that
\begin{align*}
     D(\bar x)^2
    &= - \frac{3}{2} z^T \grad^2  D(x_1)^2 z + O(\|z\|^3) .
\end{align*}

\subsection{Differentiating the fitness function}
\label{apx:H_calc}

>>>>

What are the fitness consequences?
A population of $F_2$ hybrids will begin to be substantially less fit than the parentals
once they differ from the optimum by a distance of order $\gamma$,
i.e., once $\sqrt{4 \omega T/N_e} \approx \gamma / \sigma_N$.
This implies that hybrid incompatibility among $F_2$ hybrids should appear much slower --
on a time scale of $N_e (\gamma / \sigma_N)^2 / (4 \omega)$ generations.
The $F_1$s will not suffer fitness consequences until the hybrid mean is further than $\gamma$ from the optimum;
% as shown in appendix \ref{apx:away_from_opt} 
as suggested by figure \ref{fig:conceptual_fig}, Taylor expanding $D^2$ along the optimal set implies that
this deviation of the mean from optimum grows with the square of the distance between the parental populations,
and so we expect fitness costs in $F_1$s to appear on a time scale of $N_e^2$ generations.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Local expansion of the fitness surface}
\label{apx:H_calc}
